\section{Bibliografía}
{[}1{]}  Adomavicius, G., and A. Tuzhilin. “Toward the next Generation of Re-
commender Systems: A Survey of the State-of-the-art and Possible Extensions.”

IEEE Trans. Knowl. Data Eng. IEEE Transactions on Knowledge and Data En-
gineering: 734-49. Print.

{[}2{]} Sauter, Vicki Lynn, and Vicki Lynn Sauter. Decision Support Systems

for Business Intelligence. 2nd ed. Hoboken, N.J.: Wiley, 2010. Print.

{[}3{]}  R.Bell, Y. Koren and C. Volinsky. The BellKor 2008 Solution to the

Netflix Prize. 2008

{[}4{]} Said, Alan, Brijnesh J. Jain, Sascha Narr, and Till Plumbaum. “Users and
Noise: The Magic Barrier of Recommender Systems.” User Modeling, Adapta-
tion, and Personalization Lecture Notes in Computer Science: 237-48. Print

{[}5{]}  Lantz, B. (n.d.). Machine learning with R: Learn how to use R to apply powerful machine learning methods and gain an insight into real-world applications.

{[}6{]} Harrington, P. (2012). Machine learning in action. Shelter Island, NY: Manning Publications.

{[}7{]} Toomey, D. (n.d.). R for data science.

{[}8{]} Teutonico, D. (2015). Ggplot2 essentials explore the full range of ggplot2 plotting capabilities to create meaningful and spectacular graphs. Birmingham, England: Packt Publishing.

{[}9{]}  Leipzig, J., \& Li, X. (2009). Data mashups in R. Sebastopol, Calif.: O'Reilly.

{[}10{]} Ricci, F. (2011). Recommender systems handbook. New York: Springer.

{[}11{]}  Russell, S., \& Norvig, P. (1995). Artificial intelligence: A modern approach. Englewood Cliffs, N.J.: Prentice Hall.

{[}12{]} Website Crawler Tool and Google Sitemap Generator \\
http://freetools.webmasterworld.com/tools/crawler-google-sitemap-generator/
